\LARGE \bf Longitudinal Trajectory Planning and Tracking for Fixed-Path Autonomous Driving

### 2016-01-19 paper1.tex
replace unlabeled full 7 phase diagram with the full spec version

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/7phaseprofile.png}
  \caption{7 phase constant jerk profile along curvilinear distance axis.}
  \label{fig:7phaseprofile}
\end{figure}

@@

Consider, as a starting point, the case in which a vehicle is at rest and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:7phaseprofile} shows this trajectory over time.
The problem is defined by the vector of known values $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
It is assume that the final forward acceleration will be zero.
If the magnitude of the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The remaining parameters yet to be set now become $\mathbf{a}_m = [a^+_m , a^-_m]$ and $\mathbf{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
The authors then propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\mathbf{b}$.
The other profiles are explained below in section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k, k = 1 ... N_s$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$. All impossible scenarios are automatically ruled out.

@@

A change from one speed to another. 
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen for a segment in which it is impossible to completely arrive at the end speed given the initial speed.

@@

\emph{Put kinematic equations here? Many are extrememly large, and I don't have the code. Perhaps better to summarize what was put into the symbolic solver.}

@@

The general idea will be to project the vehicle's current position onto the path then find the cumulative distance along the path between the start point and the projection point.
This will be the 1D location corresponding to the vehicle's current reference time.
Once this reference time is obtained, it may be used to look up position, speed, acceleration, and jerk along the curve of the path over the future time window.
From there it is a matter of simple geometry to transform these values into the coordinate system of the path and, subsequently, any other coordinate system which may be needed.

>>>>

\begin{figure}[thpb]
  \centering
  \includegraphics[width=1.0\columnwidth]{graphics/Full7PhaseSpecVertical.png}
  \caption{7 phase constant jerk profile along curvilinear distance axis.}
  \label{fig:full7phasespec}
\end{figure}

@@

Consider, as a starting point, the case in which a vehicle is moving at some small initial speed and needs to accelerate to some travelling speed, maintain that speed for some distance, then brake to a stop at a prescribed end location.
Figure \ref{fig:full7phasespec} shows this trajectory over time.
The problem is defined by the vector of known values $\mathbf{b}  = [v_i, a_i, L, v_m, v_f]$, being initial speed, initial acceleration, the total distance, speed limit, and the final speed, respectively.
It is assume that the final forward acceleration will be zero.
If the magnitude of the desired peak acceleration and jerk ($a_m$ and $j_m$, respectively) are known, then the profile with $M$ jerk phases (7 in this case) can be generated by solving for the time intervals $[\Delta t_1, ..., \Delta t_M]$.
Jerk and peak acceleration may be different when reducing speed versus increasing speed to more closely mirror human driving behavior \emph{Citation}.
The remaining parameters yet to be set now become $\mathbf{a}_m = [a^+_m , a^-_m]$ and $\mathbf{j}_m = [j^+_m , j^-_m]$.
There are, however, multiple solutions for $\Delta t_2$, $\Delta t_4$, and $\Delta t_6$.
The proper solution must be chosen by eliminating negative and complex solutions.
As we will show later, peak acceleration and jerk must sometimes be modified to obtain physically possible time intervals.
To enable this, ranges of acceptable longitudinal jerk and acceleration $\mathbf{a}^{max}_m = [a^{+,max}_m , a^{-,max}_m]$ and $\mathbf{j}^{max}_m = [j^{+,max}_m , j^{-,max}_m]$ are set according to the relation in Eqs. \ref{eq:am} and \ref{eq:jm}.
This is computed for every point along the path.
In the simplest case, one value for each of the quantities expressed in those relations may be chosen for the entire path.

\begin{equation}
  a^{+,max}_m >= a^+_m > 0 > a^-_m >= a^{-,max}_m
  \label{eq:am}
\end{equation}
\begin{equation}
  j^{+,max}_m >= j^+_m > 0 > j^-_m >= j^{-,max}_m
  \label{eq:jm}
\end{equation}

It is obvious that there are many cases in which this solution will fail.
For instance, if $L$ is sufficiently short and $v_m$ is sufficiently high, then it will not be possible to ever reach $v_m$ with realistic values of $\mathbf{a}_m$ and $\mathbf{j}_m$.
We propose that 4 other basic profiles be defined, and an algorithm constructed which judiciously chooses the appropriate profile for every segment defined by a vector $\mathbf{b}$.
The other profiles are explained below in Section \ref{sec:jerkprofiles}.
A path is then a set of $N_s$ segments, each of which is defined by a set of parameters $\mathbf{b}_k, k = 1 ... N_s$ and can be solved indivually in sequence.
Determination of where to break a path into segments is discussed below in Section \ref{sec:pathsegmentation}.

There are a total of five potential jerk profiles which have been created to cover all feasible values in $\mathbf{b}$. All impossible scenarios are automatically ruled out.
To find closed-form solutions for each, a symbolic solver was used. The target values for each profile are the time steps between jerk changes.
These are solved by plugging in initial conditions, default jerk values

For each of the profiles, it is possible that the chosen values of $\mathbf{a}_m$ and $\mathbf{j}_m$ will not be feasible for a desired speed at the end of the phase.
This results in negative time intervals for that phase.
In many cases, modifying $\mathbf{a}_m$ and $\mathbf{j}_m$ such that they still lie within $\mathbf{a}^{max}_m$ and $\mathbf{j}^{max}_m$ will remedy this.
Algorithm \ref{alg:modifyacceljerkpeaks} describes this procedure.
When it fails, a new jerk profile must be chosen.

\begin{figure}
  \begin{algorithmic}[1]
    \Procedure{ModifyAccelJerkPeaks}{$\Delta t$, $\mathbf{a}_m$, $\mathbf{j}_m$, $\mathbf{a}^{max}_m$, $\mathbf{j}^{max}_m$}

    \EndProcedure
  \end{algorithmic}
\caption{Procedure for modifying peak accel and jerk magnitude for rememdy negative time intervals for a given phase. This procedure is employed for each of the profiles.}
\label{alg:modifyacceljerkpeaks}
\end{figure}

\subsubsection{7 Phase} \label{sec:7phase}

This profile, described above, is always attempted first.
All time steps have a single solution, enabled by the fact that the initial and end conditions are known, and the two peak accelerations and two jerk magnitudes are provided as configuration parameters.

@@

A change from one speed to another.
All of the above profiles are composed of some combination of a 3 phase profile and a $j_k = 0$ phase.
This presents a difficulty in that either $L$ or $v_f$ may be enforced, but not both (there is no solution to enforce both).
As such, this profile is chosen for a segment in which it is impossible to completely arrive at the end speed given the initial speed.

@@

@@

The general idea is to project the vehicle's current position onto the path then find the cumulative distance along the path between the start point and the projection point.
This is the 1D location corresponding to the vehicle's current reference time.
Once this reference time is obtained, it may be used to look up position, speed, acceleration, and jerk along the curve of the path over the future time window.
From there it is a matter of simple geometry to transform these values into the coordinate system of the path and, subsequently, any other coordinate system which may be needed.
